A Motion Blur Resilient Fiducial Marker For Quadcopter Imaging

### 2014-05-30 WACV/paper.tex
1. Added Comparison on new setup 2. Commented some result on BLUT

\def\wacvPaperID{****} % *** Enter the wacv Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

\begin{figure}
\centering
 \begin{subfigure}[b]{0.19\linewidth}
  \centering
  \includegraphics[width=0.8\linewidth]{intersense.jpg}
  Circular Data Matrix~\cite{NaimarkF02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit~\cite{ARToolkit02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\quad~\cite{Fiala05}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  PiTag\quad~\cite{Pitag13}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 each code has their own pros and cons for various environments, none are
 designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

@@

\noindent\begin{figure}
\includegraphics[width=\linewidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred AR Tag and Pi--tag with various blur scales}
%\captionof{table}{Recognition rate of AR Tag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\linewidth}{|Y|Y|Y|}
\cline{1-3}
\small{Blur} & \multicolumn{2}{c|}{ \small{Recognition Rate}}
\\\cline{2-3}
\small{Scale}& \small{PiTag} &	\small{ARTag} \\ \cline{1-3}
\small{15} & \small{100} & \small{100} \\ %\cline{1-3}
\small{30} & \small{0} & \small{100} \\  %\cline{1-3}
\small{35} & \small{0} & \small{19} \\ %\cline{1-3}
\small{50} & \small{0} & \small{0} \\ \cline{1-3}
\end{tabularx}
\captionof{figure}{Figure showing PiTag and ARTag blurred with various blur
scales at different orientations. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tags are significantly reduced due to
blur. For severe blur, detection is not possible.}
\label{fig:artag_pitag}
\end{figure}

@@

We are able to find the number of rings in the fiducial by finding
number of transitions in the intensity profile. To increase the classification
accuracy, training data for patterns having same number of rings are grouped together; e.g., in two bit
binary coded fiducial, training data for pattern ``01'' and ``10'' will be
grouped together. In three bit binary coded fiducial, training data for pattern
``001'', ``010'' and ``100'' will form one group, while training data for
pattern ``110'', ``011'' and ``101'' will be in other group, and so on. 
Depending on the number of detected rings in test pattern, it is matched
against corresponding group in the training data, again using  the K-NN. 
If we detect either zero rings or maximum possible
rings in the test pattern, there will be no need to do further classification, we
can classify the pattern as class 0 or the maximum class containing all 1s.

@@

In another setup we arranged our fiducials on four sides of a box and revolved
quadcopter around it. Later, we repeated the process by replacing our fiducial
by AR Tags. Some intermediate frames are shown in Figure \ref{fig:setup}.

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_6/output_514.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_6/output_556.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_2/output_35.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_2/output_330.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_6/output_943.jpg}
\end{subfigure}
\caption{Figure showing intermediate frames captured by quadcopter while
revolving around our setup}
\label{fig:setup}
\end{figure*}
\subsubsection{Comparison with BLUT}

We also compare our approach with tracking designed for blurred input scenes.
We have used four image sequences (consisting of around 1000 frames each), each
one containing a different blur resistant fiducial pattern to test the performance of
BLUT \cite{Wu:2011} and compare it with our result on the same image sequence.
From the images in the top rows of Figure
\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}, we can see that BLUT is
able to track the fiducial when the position of fiducial does not change too
much in successive frames. Also, it can be seen that once BLUT looses 
track of the fiducial, it is not able to recover. Since our approach detects the
code in each frame, large changes in the patterns position is not an issue.
Our detection results are also shown in Figure
\ref{fig:BLUT_compare_00}-\ref{fig:BLUT_compare_11}.

@@

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/5.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output5.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``10'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. From the second frame, BLUT looses track.}
\label{fig:BLUT_compare_10}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output6.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``11'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. BLUT lost the track from third frame. There is sudden reversal of
direction from the quadcopter in the third frame. In first two frames, the quadcopter was
going up, but suddenly moved down.}
\label{fig:BLUT_compare_11}
\end{figure*}

@@

We have demonstrated the effectiveness of our blur invariant fiducial both
synthetically and on real video clips captured from a quadcopter.   Our approach obtains
approximately 86-95\% recognition rate on fiducals in real scenes compared to existing codes
that are around 64\%.  We discuss some limitations of our approach in the
section.
%\noindent\textbf{Processing Time}~~
Currently, our processing time (0.3 seconds per frame) does not provide
real-time performance.  As such, we currently envision this will be used in an
offline manner for performing analysis of flight paths. Code profiling revealed that the Gabor filtering along the eight
directions takes most of the time (0.03 -- 0.04 seconds per orientation).  Either an
improved Gabor filter scheme is required or an alternative strategy for
detection is required.
%\noindent\textbf{False Negatives}~~
We found that sometimes our detection
algorithm fails to recognize our fiducial with binary code ``00'' when there is
large amount of blur.  The is because when there is too much blur, the innermost
ring's response in the Gabor output is too low and not detected properly.
This problem can be resolved by increasing the radius of innermost ring to
reduce the effect of blur on the innermost ring. 
%\noindent\textbf{Pose Estimation}~~
We note that other markers are able to give
full pose estimation after detection.  However, we are only able to reliably detect
the center point and therefore cannot estimate pose.  Of course, if four
markers were used in a known order, pose could be estimated. The current
resolution of onboard camera will be main hurdle to clear before we can
effectively use multiple markers in each scene.
%\noindent\textbf{Number of Fiducials}~~
Currently, compared to ARTag fiducial markers, we are able to generate less
number of fiducials. Many applications in robotics (e.g. quadcopter navigation)
may not require large number of fiducial markers as available by ARTag.  Most
of the time, it is sufficient to have 4-6 different fiducial patterns. Still,
we may be able to generate a larger number of fiducials by using color
backgrounds. This is an area interest for further investigation.

>>>>

\def\wacvPaperID{1} % *** Enter the wacv Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

\begin{figure}
\centering
 \begin{subfigure}[b]{0.23\linewidth}
  \centering
  \includegraphics[width=0.8\linewidth]{intersense.jpg}
  Circular Data Matrix~\cite{NaimarkF02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
 \centering
  \includegraphics[width=\linewidth]{pattKanji.pdf}
  ARToolkit~\cite{ARToolkit02}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.12\linewidth}
  \centering
  \includegraphics[width=\linewidth]{ARtag.jpg}
  ARTag\quad~\cite{Fiala05}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.12\linewidth}
  \centering
  \includegraphics[width=\linewidth]{pifiducial.jpg}
  PiTag\quad~\cite{Pitag13}
 \end{subfigure}\quad
 \begin{subfigure}[b]{0.14\linewidth}
  \centering
  \includegraphics[width=\linewidth]{our_fiducial}
  Our Fiducial
 \end{subfigure}
 \caption{This figure shows the design of several existing fiducial markers.  While
 each code has their own pros and cons for various environments, none are
 designed to be recognized under motion blur.}
 \label{fig:previous_work}
\end{figure}

@@

\noindent\begin{figure}
\includegraphics[width=\linewidth]{artag_pitag.pdf}
%\captionof{figure}{Blurred ARTag and Pi--tag with various blur scales}
%\captionof{table}{Recognition rate of ARTag and Pi-tag fiducial marker atvarious blur scales}
\begin{tabularx}{\linewidth}{|Y|Y|Y|}
\cline{1-3}
\small{Blur} & \multicolumn{2}{c|}{ \small{Recognition Rate}}
\\\cline{2-3}
\small{Scale}& \small{PiTag} &	\small{ARTag} \\ \cline{1-3}
\small{15} & \small{100} & \small{100} \\ %\cline{1-3}
\small{30} & \small{0} & \small{100} \\  %\cline{1-3}
\small{35} & \small{0} & \small{19} \\ %\cline{1-3}
\small{50} & \small{0} & \small{0} \\ \cline{1-3}
\end{tabularx}
\captionof{figure}{Figure showing PiTag and ARTag blurred with various blur
scales at different orientations. Table on the right shows the recognition rate
(in percent) of both fiducial markers at various blur scales along all blur
orientations.  Recognition rates for both tags are significantly reduced due to
blur. For severe blur, detection is not possible.}
\label{fig:artag_pitag}
\end{figure}

@@

\begin{comment}
We are able to find the number of rings in the fiducial by finding
number of transitions in the intensity profile. To increase the classification
accuracy, training data for patterns having same number of rings are grouped together; e.g., in two bit
binary coded fiducial, training data for pattern ``01'' and ``10'' will be
grouped together. In three bit binary coded fiducial, training data for pattern
``001'', ``010'' and ``100'' will form one group, while training data for
pattern ``110'', ``011'' and ``101'' will be in other group, and so on. 
Depending on the number of detected rings in test pattern, it is matched
against corresponding group in the training data, again using  the K-NN. 
If we detect either zero rings or maximum possible
rings in the test pattern, there will be no need to do further classification, we
can classify the pattern as class 0 or the maximum class containing all 1s.
\end{comment}

@@

In another setup we arranged our fiducials on four sides of a box and revolved
quadcopter around it. Later, we repeated the process by replacing our fiducial
by ARTags. Some intermediate frames are shown in Figure \ref{fig:setup}.

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_artag/output_79.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_artag/output_150.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_artag/output_194.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_artag/output_339.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_artag/output_480.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_6/output_514.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_2/output_64.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_2/output_35.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_2/output_330.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{setup_our/output_6/output_943.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{\textwidth}
\includegraphics[width=\linewidth]{compare_detection.jpg}
\end{subfigure}
\caption{Figure showing comparison of detection of ARTag versus our fiducial
when quadcopter is revolving around our setup.
Top row shows ARTags are not getting detected while middle row shows in
similar condition our tags are getting detected. Overall detection rate of our
tags is 90\% while that of ARTags is around 60\%. In bottom, comparison of
detection of two type of tags over time is shown. We can see that ARTag is
``chopped off'' frequently while our tag is detected continuously.}
\label{fig:setup}
\end{figure*}

\subsubsection{Comparison with BLUT}

We also compare our approach with tracking designed for blurred input scenes.
We have used four image sequences (consisting of around 1000 frames each), each
one containing a different blur resistant fiducial pattern to test the performance of
BLUT \cite{Wu:2011} and compare it with our result on the same image sequence.
From the images in the top rows of Figure
\ref{fig:BLUT_compare_00} and \ref{fig:BLUT_compare_01}, we can see that BLUT is
able to track the fiducial when the position of fiducial does not change too
much in successive frames. Also, it can be seen that once BLUT looses 
track of the fiducial, it is not able to recover. Since our approach detects the
code in each frame, large changes in the patterns position is not an issue.
Some of our detection results are also shown in Figure
\ref{fig:BLUT_compare_00} and \ref{fig:BLUT_compare_01}. (Results on other two
tags are shown in supplementary material.)

@@

\begin{comment}
\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_10/5.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output1.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_10/output5.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``10'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. From the second frame, BLUT looses track.}
\label{fig:BLUT_compare_10}
\end{figure*}

\begin{figure*}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_output_11/6.jpg}
\end{subfigure}\\
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output2.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output3.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output4.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output5.jpg}
\end{subfigure}
\begin{subfigure}[b]{.19\textwidth}
\includegraphics[width=\linewidth]{BLUT_input_11/output6.jpg}
\end{subfigure}
\caption{Top: Output of BLUT~\cite{Wu:2011} on sample image sequence containing
``11'' binary coded fiducial. Bottom: Output of our algorithm on the same image
sequence. BLUT lost the track from third frame. There is sudden reversal of
direction from the quadcopter in the third frame. In first two frames, the quadcopter was
going up, but suddenly moved down.}
\label{fig:BLUT_compare_11}
\end{figure*}
\end{comment}

@@

We have demonstrated the effectiveness of our blur invariant fiducial both
synthetically and on real video clips captured from a quadcopter.   Our approach obtains
approximately 86-95\% recognition rate on fiducals in real scenes compared to existing codes
that are around 64\%.  We discuss some limitations of our approach in the
section.
%\noindent\textbf{Processing Time}~~
Currently, our processing time (0.3 seconds per frame) does not provide
real-time performance.  As such, we currently envision this will be used in an
offline manner for performing analysis of flight paths. Code profiling revealed
that the Gabor filtering along the eight directions takes most of the time
(0.03 -- 0.04 seconds per orientation).  Either an improved Gabor filter scheme
is required or an alternative strategy for detection is required.
%\noindent\textbf{False Negatives}~~
We found that sometimes our detection
algorithm fails to recognize our fiducial with binary code ``00'' when there is
large amount of blur.  The is because when there is too much blur, the innermost
ring's response in the Gabor output is too low and not detected properly.
This problem can be resolved by increasing the radius of innermost ring to
reduce the effect of blur on the innermost ring. 
%\noindent\textbf{Pose Estimation}~~
We note that other markers are able to give
full pose estimation after detection.  However, we are only able to reliably detect
the center point and therefore cannot estimate pose.  Of course, if four
markers were used in a known order, pose could be estimated. The current
resolution of onboard camera will be main hurdle to clear before we can
effectively use multiple markers in each scene.
%\noindent\textbf{Number of Fiducials}~~
Currently, compared to ARTag fiducial markers, we are able to generate less
number of fiducials. Many applications in robotics (e.g. quadcopter navigation)
may not require large number of fiducial markers as available by ARTag.  Most
of the time, it is sufficient to have 4-6 different fiducial patterns. Still,
we may be able to generate a larger number of fiducials by using color
backgrounds. This is an area of interest for further investigation.
